\documentclass[12pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{inputenc}
\usepackage[T1]{fontenc}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

\title{\textbf{Feasibility Report}\\[0.5em]
       \large Budget Buddy Project}
\author{Prepared by: Your Name}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\newpage

%--- Introduction ---
\section{Introduction}
This report evaluates the feasibility of the \textbf{Budget Buddy} application. It examines the technical, operational, economic, and legal aspects of the project, and outlines both functional and non-functional requirements.

%--- Project Overview ---
\section{Project Overview}
Budget Buddy is a personal finance management tool built with React Native (Expo) and TypeScript. It helps users track income, expenses, set budgets, and visualize financial data through interactive charts.

%--- Functional Requirements ---
\section{Functional Requirements}

\begin{enumerate}[label=\textbf{FR\arabic*:}, leftmargin=*, itemsep=0.5em]

  \item \textbf{User Authentication}
        \begin{itemize}
            \item Users can register with email and password.
            \item Users can log in and log out securely.
            \item Password reset via email link.
        \end{itemize}

  \item \textbf{Expense Management}
        \begin{itemize}
            \item Add, edit, and delete expense entries.
            \item Categorize expenses (e.g., Food, Transport).
            \item Attach optional receipt images.
        \end{itemize}

  \item \textbf{Income Management}
        \begin{itemize}
            \item Record income sources and amounts.
        \end{itemize}

  \item \textbf{Budget Creation}
        \begin{itemize}
            \item Define monthly budgets per category.
            \item Visual warnings when spending exceeds the budget.
        \end{itemize}

  \item \textbf{Reporting and Analytics}
        \begin{itemize}
            \item Generate daily, weekly, and monthly summary reports.
            \item Display charts for expense distribution.
        \end{itemize}

  \item \textbf{Data Synchronization}
        \begin{itemize}
            \item Sync data across devices via cloud backend (e.g., Firebase).
        \end{itemize}

  \item \textbf{Settings}
        \begin{itemize}
            \item Theme selection (light/dark).
            \item Currency selection.
        \end{itemize}

\end{enumerate}

%--- Non-Functional Requirements ---
\section{Non-Functional Requirements}

\begin{enumerate}[label=\textbf{NFR\arabic*:}, leftmargin=*, itemsep=0.5em]

  \item \textbf{Performance}
        \begin{itemize}
            \item App launch time under 2 seconds on modern devices.
            \item UI interactions respond within 100 ms.
        \end{itemize}

  \item \textbf{Scalability}
        \begin{itemize}
            \item Backend must support up to 10,000 concurrent users.
        \end{itemize}

  \item \textbf{Security}
        \begin{itemize}
            \item Data encrypted at rest and in transit (HTTPS/TLS).
            \item Secure authentication using OAuth2 or JWT.
        \end{itemize}

  \item \textbf{Usability}
        \begin{itemize}
            \item Intuitive UI adhering to Material Design guidelines.
            \item Accessible to users with visual impairments (WCAG 2.1 AA).
        \end{itemize}

  \item \textbf{Reliability}
        \begin{itemize}
            \item 99.9\% uptime for cloud services.
            \item Automatic data backup with versioning.
        \end{itemize}

  \item \textbf{Maintainability}
        \begin{itemize}
            \item Codebase follows clean architecture and TypeScript strict typing.
            \item Comprehensive unit and integration test coverage of at least 80\%.
        \end{itemize}

  \item \textbf{Portability}
        \begin{itemize}
            \item Runs on iOS 13+ and Android 8+ devices.
        \end{itemize}

  \item \textbf{Legal and Compliance}
        \begin{itemize}
            \item GDPR compliant data handling for EU users.
            \item Provide privacy policy and terms of service.
        \end{itemize}

\end{enumerate}

%--- Feasibility Analysis ---
\section{Feasibility Analysis}

\subsection{Technical Feasibility}
The chosen stack -- React Native with Expo, TypeScript, and Firebase -- is mature,
well-documented, and supported across platforms. Existing libraries cover most
functional requirements, reducing development effort significantly.

\subsection{Operational Feasibility}
Users can install the app from app stores. Cloud backend services offer managed
authentication, database, and storage, simplifying operations and ongoing maintenance.

\subsection{Economic Feasibility}
Estimated development effort: 3 developers $\times$ 4 months $\approx$ 480 person-hours.

\medskip
\noindent Cost breakdown (approximate):
\begin{itemize}
  \item Development labor: \$30,000
  \item Cloud services (Firebase Blaze tier): \$50--\$100/month (scalable)
  \item App Store fees: \$25 (Apple), \$25 (Google)
\end{itemize}

\noindent Total initial cost is under \$35,000, which is reasonable for a small-scale
mobile SaaS product.

\subsection{Legal Feasibility}
Data handling complies with GDPR by anonymizing personal identifiers and providing
user data export and delete features. A clear privacy policy will be published before
launch.

%--- Conclusion ---
\section{Conclusion}
The Budget Buddy project is feasible across technical, operational, economic, and legal
dimensions. The outlined functional and non-functional requirements provide a clear
roadmap for implementation. We recommend proceeding to the development phase.

\end{document}
